\section{Future Trends}
Finally, let's discuss all the potential future trends of Autonomous Navigation and Metaverse:
\\\\
1.	Autonomous Navigation \cite{autonomousFuture}
\\\\
(1)	Ability to Learn Driver’s Routines and Preferences

Driverless cars can leverage their machine learning capabilities to learn the routines and preferences of their passengers. For example, providing greater assistance by automatically performing routine tasks such as ensuring on-time arrival for work or appointments, finding a cheap parking spot in dense cities, or preferentially driving to stores where specific, desired products are in stock.
\\\\
(2) Enhance Driving Safety

After solving the challenges of autonomous navigation. We can soon arrive at our destination by choosing the fastest and safest route.
\\\\
(3)	In-Vehicle Advertising

Advertising will be a big part of the experience at some point. While on the way to your destination, you’ll be able to add a stop for shopping or food, and companies will be vying for that recommendation. Briefly, you’ll be able to see the extra time needed and be able to order in transit.
\\\\
(4)	Better Privacy and Cybersecurity Features

Future driverless cars will \textbf{incorporate more privacy and security features}. Firewalls in cars will be normalized. Protection of the driver’s data will become paramount, and it will likely be regulated.
\\\\
(5)	Multi-Internet Communications Systems

Future driverless cars will be able to communicate with each other as well as with retailers and restaurants, enabling curbside and drive-through pickups. Authorized e-commerce companies will be able to access and deliver items directly to the vehicle’s trunk.
\\\\
2.	Metaverse
\\\\
(1)	New Mode for Online Shopping \cite{metaverseFuture1}

\textbf{Consumers will no longer need to frequent physical stores to try new products before purchasing}. VR and AR experiences will allow exploration of brands and their offerings from the comfort of customers’ homes. On the other hand, the metaverse will also enable more interactive in-store experiences.
\\\\
(2)	Own and Trade Properties in Metaverse \cite{metaverseFuture2}

\textbf{Once you own something in the metaverse, it can be sold or traded to one of the other users}. This adds an element of wealth and prestige to an otherwise detached world. Some lots are worth more than others, some items are rare while others are common — all of this adds up to the creation of an economy that applies to a particular metaverse.
\\\\
(3)	Changing How We Live and Interact \cite{metaverseFuture2}

Metaverse can become \textbf{a place almost capable of replacing reality}. We’re not quite there yet (and we won’t be for years), but the efforts of companies like Meta or VRChat are bringing us closer to this than we’ve ever been before. In a perfect metaverse, you can interact with every person around you and perhaps work, study, meet friends, or even form a study group in a virtual library inside the metaverse.